User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval

### 2013-10-04 writeups/proposal/proposal.tex
apa6 formatting changes
Former-commit-id: 6d929863507f25c4c04103472b91b51cd879182c [formerly 31da54f90694d1585ce4ece60138c0ce3be3bfd1]
Former-commit-id: bdf25a16e7b821b2b555cccc3c0ba41174ba1743

@@

@@

\title{User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and Bayesian models of tag retrieval}
\shorttitle{Tag prediction on Twitter and StackOverflow}

@@

@@

\begin{document}
\maketitle

@@

@@

\begin{figure}[!htbp]
  {%
    \setlength{\fboxsep}{0pt}%
    \setlength{\fboxrule}{1pt}%
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample1-crop.pdf}}}
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample3-crop.pdf}}}
    \hfill
    \vfill
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample4-crop.pdf}}}
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample5-crop.pdf}}}
    \hfill
    \caption{Example tweets on Twitter.com}
    \label{figTweetExample}
  }%
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.4}{\resizebox{\linewidth}{!}{\includegraphics{google+HashtagExample-crop.pdf}}}
  \caption{Example post on Google+. The system recommended \emph{\#SFGiants} and \emph{\#BusterPosey} as hashtags for the user-created post}
  \label{figGoogle+Hashtags}
\end{figure}

The workflow and user interface provided for recommending hashtags for Google+ is similar to how a hashtag recommendation system for Twitter might look.
When generating content on Google+, the system automatically associates the most likely relevant hashtags with that post.
The user is free to remove any or all of the tags that the system has associated with the post, and can also use tags that were not included in the recommended set.

@@

\begin{table}[!ht]
  \caption{ACT-R Declarative Memory Model}
  \label{tabACT-RModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Activation &	 	$A_{i} = B_{i} + \sum_{j \in c}^{} W_{j} S_{ji}$ \\
      Attentional Weight &	$W_{j} = \frac{W}{n}$ \\
      Base Level & 		$B_{i} = log \sum_{j=1}^{n} {t_{j}}^{-d}$ \\
      Constant Base Level &	$B_{i} = log \frac{p(i)}{p(\overline{i})}$ \\
      Strength of Association &	$S_{ji} = log \frac{p(i|j)}{p(i|\overline{j})} \approx log \frac{p(i|j)}{p(i)}$ \\
      Recall Probability &	$P_{i} = \left( 1 + e^{\frac{\tau - A_{i}}{s}} \right )^{-1}$ \\
      \hline
    \end{tabu}
  }
\end{table}

@@

\begin{table}[!ht]
  \caption{Random Permutation Model}
  \label{tabRandPermModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Activation &		$A_{i} = r(m_{C},m_{i})$ \\
      Memory Vector &		$m_{i} = \sum_{i \in all past} c_{i} + \sum_{i \in all past} \sum_{l \in locations} o_{i,l}$ \\
      Unordered Context &	$c_{i} = e_{i}$ \\
      Ordered Context &		$o_{i,l} = e_{i^{-l}}$ \\
      Context Memory Vector &	$m_{C} = \sum_{i \in C} c_{i} + \sum_{i \in C} \sum_{l \in locations} o_{i,l}$ \\
      Environment Vector & 	$e_{i} = rand$ \\
      \hline
    \end{tabu}
  }
\end{table}

@@

\begingroup
\setstretch{1}
\setlength\bibitemsep{12pt}
\printbibliography
\endgroup

>>>>

% ref: http://tex.stackexchange.com/questions/28516/how-to-change-the-title-of-toc
\addto\captionsamerican{% Replace ``english'' with the language you use
  \renewcommand{\contentsname}%
  {Table of Contents}%
}

@@

% ref: http://tex.stackexchange.com/questions/48509/insert-list-of-figures-in-the-table-of-contents
\usepackage[nottoc,numbib]{tocbibind}

@@

\title{User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval}
%\shorttitle{Tag prediction on Twitter and StackOverflow}
\shorttitle{}

@@

\begin{document}

@@

\maketitle

@@

\listoftables
\newpage

\listoffigures
\newpage

@@

\begin{figure}[!htbp]
  {%
    \setlength{\fboxsep}{0pt}%
    \setlength{\fboxrule}{1pt}%
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample1-crop.pdf}}}
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample3-crop.pdf}}}
    \hfill
    \vfill
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample4-crop.pdf}}}
    \hfill
    \subfigure[]{\fbox{\includegraphics[width=8cm]{twitterTweetExample5-crop.pdf}}}
    \hfill
    \caption{Example tweets on twitter.com}
    \label{figTweetExample}
  }%
\end{figure}

@@

\begin{figure}[!htbp]
  \scalebox{.4}{\resizebox{\linewidth}{!}{\includegraphics{google+HashtagExample-crop.pdf}}}
  \caption{Example post on Google+}
  \label{figGoogle+Hashtags}
\end{figure}

The workflow and user interface provided for recommending hashtags for Google+ is similar to how a hashtag recommendation system for Twitter might look.
When generating content on Google+, the system automatically associates the most likely relevant hashtags with that post.
For the example in Figure \ref{figGoogle+Hashtags}, the system recommended \emph{\#SFGiants} and \emph{\#BusterPosey} as hashtags for the user-created post.
The user is free to remove any or all of the tags that the system has associated with the post, and can also use tags that were not included in the recommended set.

@@

\begin{table}[!ht]
  \caption{ACT-R declarative memory model}
  \label{tabACT-RModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Activation &	 	$A_{i} = B_{i} + \sum_{j \in c}^{} W_{j} S_{ji}$ \\
      Attentional Weight &	$W_{j} = \frac{W}{n}$ \\
      Base Level & 		$B_{i} = log \sum_{j=1}^{n} {t_{j}}^{-d}$ \\
      Constant Base Level &	$B_{i} = log \frac{p(i)}{p(\overline{i})}$ \\
      Strength of Association &	$S_{ji} = log \frac{p(i|j)}{p(i|\overline{j})} \approx log \frac{p(i|j)}{p(i)}$ \\
      Recall Probability &	$P_{i} = \left( 1 + e^{\frac{\tau - A_{i}}{s}} \right )^{-1}$ \\
      \hline
    \end{tabu}
  }
\end{table}

@@

\begin{table}[!ht]
  \caption{Random permutation model}
  \label{tabRandPermModel}
  {\tabulinesep=1.2mm
    \begin{tabu}{ll}
      \hline
      Common Name &  Equation \\
      \hline
      Activation &		$A_{i} = r(m_{C},m_{i})$ \\
      Memory Vector &		$m_{i} = \sum_{i \in all past} c_{i} + \sum_{i \in all past} \sum_{l \in locations} o_{i,l}$ \\
      Unordered Context &	$c_{i} = e_{i}$ \\
      Ordered Context &		$o_{i,l} = e_{i^{-l}}$ \\
      Context Memory Vector &	$m_{C} = \sum_{i \in C} c_{i} + \sum_{i \in C} \sum_{l \in locations} o_{i,l}$ \\
      Environment Vector & 	$e_{i} = rand$ \\
      \hline
    \end{tabu}
  }
\end{table}

@@

\begingroup
\setstretch{1}
\setlength\bibitemsep{12pt}
\clearpage
\printbibliography[heading=bibintoc]
\endgroup
